Non-kissing complexes and tau-tilting \\ for gentle algebras

### 2018-07-13 firstPaper/corrections/replyToReferee.txt

(a) In Notation 1.50, the equalities were wrong and have been corrected.

(b) We have added some details (in a new Proposition 2.24) explaining why the non-kissing facets are finite. In doing so, we had to slightly reorganise Subsection 2.2.2 (new Lemma 2.23 was previously part of the proof of Proposition (renumbered) 2.28)

* In the introduction, and in the introductory paragraphs of several sections
  the authors are sometimes quite abrupt and discuss notions that have not been
  introduced yet. For example examples this happens in
  - page 1, line 2: non-kissing paths
  - page 43: $\mathcal{L}_{nk}(\overline{Q})$
  Could this notions be introduces, at least vaguely, before using them?

  Reply: page 43: We have added a reference to the definition.

@@

* page 24 intro: ``the operation of flip''

  Reply: Done

* Example 2.2 and many more occurrences: Through the paper there is a recurring
  example and the authors decided to name it by $Q_{exm}$ et similia.
  This makes it look like it is some sort of notation when it is not. I would
  suggest to remove this convention and to just refer to it as the recurring
  example or the example in figure 15.

  Reply: We have removed all appearances of _{exm}, and replaced them by references to the relevant figures.

@@

* Just below: ``See Figure 15'' is not needed here

  Reply:

* bottom of page 24 what is a non-kissing cycle? Do you mean not self-kissing?

  Reply: That was a mistake. Thank you for spotting it! We meant non-oriented cycle.

@@

* Figure 17: $Q_{pa}$ as above why is an example given a notation-like name?

  Reply: $Q_pa$ is now replaced by the more traditional $\overrightarrow{A_n}$.

@@

* proof of 2.21: ``follow'' is not really clear here

  Reply:

* def 2.36: is any flip either increasing or decreasing?

  Reply: Yes. This has now been made axplicit and we have added the definition of decreasing.

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
separation figures
corrections

% others
\newcommand{\fref}[1]{Figure~\ref{#1}} % reference figures
\newcommand{\ie}{\textit{i.e.}~} % id est
\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
\newcommand{\Eg}{\textit{E.g.}~} % exempli gratia
\newcommand{\apriori}{\textit{a priori}} % a priori
\newcommand{\viceversa}{\textit{vice versa}} % vice versa
\newcommand{\versus}{\textit{vs.}~} % versus
\newcommand{\aka}{\textit{a.k.a.}~} % also known as
\newcommand{\perse}{\textit{per se}} % per se
\newcommand{\ordinal}{\textsuperscript{th}} % th for ordinals
\newcommand{\ordinalst}{\textsuperscript{st}} % st for ordinals
\definecolor{darkblue}{rgb}{0,0,0.7} % darkblue color
\definecolor{green}{RGB}{57,181,74} % green color
\definecolor{violet}{RGB}{147,39,143} % violet color
\newcommand{\darkblue}{\color{darkblue}} % darkblue command
\newcommand{\defn}[1]{\textsl{\darkblue #1}} % emphasis of a definition
\newcommand{\para}[1]{\medskip\noindent\textbf{#1.}} % paragraph
\renewcommand{\topfraction}{1} % possibility to have one page of pictures
\renewcommand{\bottomfraction}{1} % possibility to have one page of pictures
%\renewcommand\labelitemi{$\diamond$} % redefine itemize default symbol
\newcommand{\ex}{_{\textrm{exm}}} % examples
\newcommand{\pa}{_{\textrm{pa}}} % path

@@

\begin{proposition}
\label{prop:morphismsStringModules}
Let~$\rho$ and~$\rho'$ be two strings for a string algebra~$A$.
Then the dimension of the $k$-vector space~$\Hom{A} \big( M(\rho), M(\rho') \big)$ is equal to the number of pairs~$(\sigma, \sigma')$, where~$\sigma$ and~$\sigma'$ are substrings of~$\rho$ and~$\rho'$, respectively, such that there is an equality of strings~$\sigma' = \sigma^{\pm 1}$.

% \[
% \sum\limits_{\xi \text{ string}} \begin{array}{l} (\#\textrm{ of substrings equal to~$\xi$ on top of~$\rho$}) \; \cdot \\ \hspace{2cm}(\#\textrm{ of substrings equal to~$\xi$ or~$\xi^{-1}$ at the bottom of~$\rho'$}).\end{array}
% \]
\end{proposition}

@@

This section focuses on the non-kissing complex of a gentle bound quiver, defined as the clique complex of a non-kissing relation among walks in a blossoming version of the quiver~(\ref{sec:blossomingQuivers}).
We prove combinatorially that this complex is a pseudomanifold~(\ref{sec:nonKissingComplex}), introducing along the way the definitions of distinguished walks, arrows and substrings~(\ref{subsec:distinguished}) and the operation of flips~(\ref{subsec:flips}) that will be fundamental tools all throughout the paper.
We then prove the motivating result of this paper, namely that the support $\tau$-tilting complex is isomorphic to the non-kissing complex for any gentle bound quiver~(\ref{sec:nkcvsttc}).

@@

\begin{example}
A gentle bound quiver~$\bar Q\ex$ and its blossoming gentle bound quiver~$\bar Q\ex\blossom$ are represented in \fref{fig:exmBlossomingQuiver}.
\end{example}

The following lemma is immediate and left to the reader.
% See \fref{fig:exmBlossomingQuiver}.

@@

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.6]{exmBlossomingQuiver}}
	\caption{A gentle bound quiver~$\bar Q\ex$~(left) and its blossoming gentle bound quiver~$\bar Q\blossom\ex$~(right). Blossom vertices are white and blossom edges are thin.}
	\label{fig:exmBlossomingQuiver}
\end{figure}

@@

\begin{definition}
A \defn{walk} of~$\bar Q$ is a maximal string in~$\bar Q\blossom$ (thus joining two blossom vertices of~$\bar Q\blossom$).
We denote by~$\walks(\bar Q)$ the set of all walks on~$\bar Q$.
Note that~$\walks(\bar Q)$ is finite if and only if~$\bar Q$ has a relation in any non-kissing cycle.
As for strings, we often implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and we let~$\walks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \walks(\bar Q)}$ denote the set of undirected~walks.
\end{definition}

\begin{example}
\fref{fig:exmFacet} shows examples of walks on the gentle quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}.
\end{example}

@@

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=1.5]{exmBijectionAssociahedron}}
	\caption{An oriented path~$\bar Q\pa$ is simultaneously a triangulation and a grid bound quiver (top). A facet of the reduced non-kissing complex~$\RNKC[\bar Q\pa]$ can be seen as a triangulation or as a collection of non-kissing south-east paths (bottom).}
	\label{fig:exmBijectionAssociahedron}
\end{figure}

@@

\begin{example}
\fref{fig:exmFacet}~(left) gives examples of kissing and non-kissing walks.
%
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.6]{exmFacet}}
	\caption{(Left) Three walks on the quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}: the dotted red and orange walks are non-kissing, but both kiss the plain blue walk. (Right) A maximal collection~$F\ex$ of pairwise non-kissing walks on the quiver~$\bar Q\ex$: the thin light blue walks are straight, the others~are~bending.}
	\label{fig:exmFacet}
\end{figure}
\end{example}

@@

\begin{example}
\fref{fig:exmFacet}\,(right) shows a facet~$F\ex$ of the non-kissing complex~$\NKC[\bar Q\ex]$ for the quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}.
The reduced non-kissing complexes of all connected gentle bound quivers with~$2$ vertices are illustrated on \fref{fig:all2}.
The reduced non-kissing complexes of two gentle bound quivers with~$3$ vertices are illustrated on \fref{fig:exmNKC}\,(left).
\end{example}

@@

\begin{remark}
Note that the countercurrent order~$\prec_\alpha$
\begin{itemize}
\item is well-defined: if both endpoints of~$\sigma$ are in~$Q_0$, then $\mu_\star$ (resp.~$\nu_\star$) enters and exits~$\sigma$ in the same direction since~$\mu_\star$ and~$\nu_\star$ are non-kissing;
\item is independent of the orientation of~$\mu_\star$ and~$\nu_\star$:~$\mu_\star \prec_\alpha \nu_\star$ iff $(\mu_\star)^{-1} \prec_\alpha \nu_\star$ iff $\mu_\star \prec_\alpha (\nu_\star)^{-1}$; we thus also consider~$\prec_\alpha$ as a relation on undirected marked walks;
\item depends on which occurrence of~$\alpha$ is marked on~$\mu$ and~$\nu$.
\end{itemize}
\end{remark}

@@

\begin{proof}
We prove that~$\prec_\alpha$ is transitive.
Let~$\lambda_\star$, $\mu_\star$, $\nu_\star$ be three pairwise non-kissing walks marked at an occurrence of~$\alpha$ such that~${\lambda_\star \prec_\alpha \mu_\star \prec_\alpha \nu_\star}$. Let~$v$ be a vertex where~$\lambda_\star$ and~$\mu_\star$ split. Then
%Let~$\sigma$ (resp.~$\tau$, resp.~$\rho$) denote the common substring of~$\lambda_\star$ and~$\mu_\star$ (resp.~of~$\mu_\star$ and~$\nu_\star$, resp.~of~$\lambda_\star$ and~$\nu_\star$) containing that occurrence of~$\alpha$. We distinguish two situations:
\begin{itemize}
\item either~$\nu_\star$ contains~$v$, then it must leave~$v$ via the same arrow as~$\mu_\star$ (otherwise~$\nu_\star \prec_\alpha \mu_\star$), so that~$\lambda_\star \prec_\alpha \nu_\star$.
\item or~$\nu_\star$ does not contain~$v$, then~$\nu_\star$ and~$\mu_\star$ split at a vertex~$w$ between~$\alpha$ and~$v$. Since~${\mu_\star \prec_\alpha \nu_\star}$, $\mu$ (and thus~$\lambda$) leaves~$w$ with an arrow in the same direction as~$\alpha$, while~$\nu$ leaves~$w$ with an arrow opposite to the direction of~$\alpha$, so that~$\lambda_\star \prec_\alpha \nu_\star$.
\end{itemize}
Moreover, $\prec_\alpha$ is antisymmetric by definition.
Finally, any two distinct walks of~$F$ marked at an occurrence of~$\alpha$ are comparable in~$\prec_\alpha$.
Therefore, the reflexive closure of~$\prec_\alpha$ defines a total order on the walks of~$F$ marked at an occurrence of~$\alpha$.
\end{proof}

@@

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.6]{exmFlip}}
	\caption{The flip of the orange walk~$\omega$ in the facet~$F\ex$ of \fref{fig:exmFacet}. The other two walks~$\mu, \nu$ of~$F\ex$ involved in the flip are the yellow and green walks. The distinguished arrows on each walk of~$F\ex$ are marked with triple arrows.}
	\label{fig:exmFlip}
\end{figure}
\end{example}

@@

\begin{definition}
\label{def:increasingFlip}
If the common substring~$\sigma$ of~$\omega$ and~$\omega'$ is on top of~$\omega$ and at the bottom of~$\omega'$, then we say that the flip~$F \to F'$ is \defn{increasing} and that the common substring~$\sigma$ is an \defn{ascent} of~$F$ and a \defn{descent} of~$F'$.
We denote by ${\ascents(F) \subseteq \strings^\pm(\bar Q)}$ and $\descents(F) \subseteq \strings^\pm(\bar Q)$ the sets of ascents and descents of~$F$ respectively.
%In the opposite situation, the flip is \defn{decreasing} and~$\sigma$ is a descent of~$F$ and an ascent of~$F'$.
\end{definition}

@@

\begin{example}
Oriented flip graphs were studied carefully in~\cite{GarverMcConville, MannevillePilaud-accordion, McConville} for the dissection and grid bound quivers introduced in Section~\ref{subsec:dissectionGridQuivers}.
Note that when the quiver is an oriented path~$\bar Q\pa$, a flip in a facet of the non-kissing complex~$\NKC[\bar Q\pa]$ corresponds to the classical flip of a diagonal in the corresponding triangulation (see \fref{fig:exmBijectionAssociahedron}).
Moreover, the flip is increasing if and only if the slope of the diagonal increases along the flip.
\end{example}

@@

In fact, our proof of Theorem~\ref{thm:lattice} is an adaptation of the proof  developed by T.~McConville in~\cite{McConville}.
Namely, we define a closure operator on subsets of strings whose biclosed sets have a lattice structure~(\ref{sec:biclosedStrings}), define a natural lattice congruence on biclosed sets~(\ref{sec:latticeCongruence}), and show that the Hasse diagram of the lattice quotient is isomorphic to the non-kissing oriented flip graph~(\ref{sec:biclosedSetsToNKF}).
Finally (\ref{sec:nonFriendlyComplex}), we study the join-irreducible elements of~$\NKL$ and the canonical join complex of~$\NKL$ which we call the non-friendly complex as in~\cite{GarverMcConville-grid}.

@@

\begin{definition}
A \defn{join-representation} of~$x \in L$ is a subset~$J \subseteq L$ such that~${x = \bigJoin J}$.
Such a representation is \defn{irredundant} if~$x \ne \bigJoin J'$ for any strict subset~$J' \subsetneq J$.
The irredundant join-representations of an element~$x \in L$ are ordered by containement of the lower ideals of their elements, \ie~$J \le J'$ if and only if for any~$y \in J$ there exists~$y' \in J'$ such that~$y \le y'$ in~$L$.
The \defn{canonical join-representation} of~$x$ is the minimal irredundant join-representation of~$x$ for this order when it exists.
The \defn{canonical meet-representation} is defined dually.
\end{definition}

@@

\begin{enumerate}
\item We have $R \cup \closure{(\closure{\{\sigma\}} \cup \closure{\{\tau\}} )} =   R \cup \closure{\{\sigma,\tau\}}$.
Condition (ii) thus shows that $R \cup \closure{\{\sigma,\tau\}}$ is biclosed.
It follows that $S\vee T = R \cup \closure{\{\sigma,\tau\}}$.

@@

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.45]{exmBiclosed}}
	\caption{Four sets of strings on the gentle bound quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}\,(left). The first is neither closed not coclosed, the second is closed but not coclosed, the third is coclosed but not closed, and the fourth is biclosed.}
	\label{fig:exmBiclosed}
\end{figure}
\end{example}

@@

\begin{proof}
The proof is inspired from that of~\cite[Thm.~6.5]{McConville}.
The main difficulty is that~$\Bicl{\bar Q}$ does not satisfies Condition~(i) of Theorem~\ref{thm:characterizationCongruenceUniform} when~$\bar Q$ has a loop.
For example, for the quiver~$\bar Q$ with a single vertex~$v$, a loop~$\alpha$, and the relation~$\alpha^2 = 0$, the biclosed sets of strings are precisely~$\varnothing$ and~$\{\varepsilon_v, \alpha\}$.
We therefore need the adapted criterion of Theorem~\ref{thm:characterizationCongruenceUniform2}.
For a string~$\sigma \in \strings^\pm(\bar Q)$, the closure~$\closure{\{\sigma\}}$ can be of two types:
\begin{itemize}
\item if there is a loop~$\alpha \in Q_1$ such that~$\sigma \alpha \in \strings^\pm(\bar Q)$, then~$\closure{\{\sigma\}} = \{\sigma, \sigma \alpha \sigma^{-1}\}$,
\item otherwise, $\closure{\{\sigma\}} = \{\sigma\}$.
\end{itemize}
In particular, for any two strings~$\sigma, \tau$, the equality~$\closure{\{\sigma\}}=\closure{\{\tau\}}$ implies $\sigma=\tau$.
We note that $\strings^\pm(\bar Q)$ is partially ordered by:~$\sigma \vartriangleleft \tau$ if and only if~$\sigma$ is a substring of~$\tau$.

@@

\begin{figure}[h]
	\capstart
	\centerline{
	\begin{overpic}[scale=.45]{exmProjections}
			\put(30,6){$\longleftarrow$}
			\put(31,8){$\projDown$}
			\put(68,6){$\longrightarrow$}
			\put(69,8){$\projUp$}
			\put(12,-3){$\projDown(S\ex)$}
			\put(50,-3){$S\ex$}
			\put(85,-3){$\projUp(S\ex)$}
	\end{overpic}
	}
	\vspace{.3cm}
	\caption{A biclosed set of strings~$S\ex \in \Bicl{\bar Q\ex}$ (middle) and its images~$\projDown(S\ex)$ (left) and~$\projUp(S\ex)$ (right) by the down and up projections of Definition~\ref{def:downUpProjections}. For space reasons, $\projUp(S\ex)$ is only represented partially: the remaining strings are obtained by adding independently the two dotted arrows to all strings containing their left endpoint.}
	\label{fig:exmProjections}
\end{figure}
\end{example}

@@

\begin{example}
The map~$\eta$ is illustrated on \fref{fig:exmSurjection}\,(left) for the gentle bound quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}\,(left).

\begin{figure}[h]
	\capstart
	\centerline{
	\begin{overpic}[scale=.45]{exmSurjection}
			\put(28,8){$\longrightarrow$}
			\put(29,10){$\eta$}
			\put(69,8){$\longrightarrow$}
			\put(70,10){$\zeta$}
			\put(13,-3){$S\ex$}
			\put(46,-3){$\eta(S\ex)$}
			\put(77,-3){$\zeta(\eta(S\ex)) = \projDown(S\ex)$}
	\end{overpic}
	}
	\vspace{.3cm}
	\caption{The maps~$\eta$ of Definition~\ref{def:eta} from biclosed sets to non-kissing facets (left) and $\zeta$ of Definition~\ref{def:zeta} from non-kissing facets to biclosed sets (right).}
	\label{fig:exmSurjection}
\end{figure}
\end{example}

@@

\begin{example}
The map~$\zeta$ is illustrated on \fref{fig:exmSurjection}\,(right)  for the gentle bound quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}\,(left).
\end{example}

@@

\begin{example}
The maps~$\eta$ and~$\zeta$ are illustrated on \fref{fig:exmSurjection}\,(right).
Compare~$\zeta(\eta(S\ex))$ on \fref{fig:exmSurjection}\,(right) with the down projection~$\projDown(S\ex)$ on \fref{fig:exmProjections}\,(left).
\end{example}

@@

\begin{definition}
We call \defn{non-kissing lattice} and denote by~$\NKL$ the transitive closure of the non-kissing oriented flip graph~$\NKG$.
\end{definition}

>>>>

% others
\newcommand{\fref}[1]{Figure~\ref{#1}} % reference figures
\newcommand{\ie}{\textit{i.e.}~} % id est
\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
\newcommand{\Eg}{\textit{E.g.}~} % exempli gratia
\newcommand{\apriori}{\textit{a priori}} % a priori
\newcommand{\viceversa}{\textit{vice versa}} % vice versa
\newcommand{\versus}{\textit{vs.}~} % versus
\newcommand{\aka}{\textit{a.k.a.}~} % also known as
\newcommand{\perse}{\textit{per se}} % per se
\newcommand{\ordinal}{\textsuperscript{th}} % th for ordinals
\newcommand{\ordinalst}{\textsuperscript{st}} % st for ordinals
\definecolor{darkblue}{rgb}{0,0,0.7} % darkblue color
\definecolor{green}{RGB}{57,181,74} % green color
\definecolor{violet}{RGB}{147,39,143} % violet color
\newcommand{\darkblue}{\color{darkblue}} % darkblue command
\newcommand{\defn}[1]{\textsl{\darkblue #1}} % emphasis of a definition
\newcommand{\para}[1]{\medskip\noindent\textbf{#1.}} % paragraph
\renewcommand{\topfraction}{1} % possibility to have one page of pictures
\renewcommand{\bottomfraction}{1} % possibility to have one page of pictures
%\renewcommand\labelitemi{$\diamond$} % redefine itemize default symbol
\newcommand{\exmAn}{\overrightarrow{A_n}} % path

@@

\begin{proposition}
\label{prop:morphismsStringModules}
Let~$\rho$ and~$\rho'$ be two strings for a string algebra~$A$.
Then the dimension of the $k$-vector space~$\Hom{A} \big( M(\rho), M(\rho') \big)$ is equal to
\[
\sum\limits_{\xi \text{ string}} \begin{array}{l} (\#\textrm{ of substrings equal to~$\xi$ on top of~$\rho$}) \; \cdot \\ \hspace{2cm}(\#\textrm{ of substrings equal to~$\xi$ or~$\xi^{-1}$ at the bottom of~$\rho'$}).\end{array}
\]
\end{proposition}

@@

This section focuses on the non-kissing complex of a gentle bound quiver, defined as the clique complex of a non-kissing relation among walks in a blossoming version of the quiver~(\ref{sec:blossomingQuivers}).
We prove combinatorially that this complex is a pseudomanifold~(\ref{sec:nonKissingComplex}), introducing along the way the definitions of distinguished walks, arrows and substrings~(\ref{subsec:distinguished}) and the operation of flip~(\ref{subsec:flips}) that will be fundamental tools all throughout the paper.
We then prove the motivating result of this paper, namely that the support $\tau$-tilting complex is isomorphic to the non-kissing complex for any gentle bound quiver~(\ref{sec:nkcvsttc}).

@@

\begin{example}
A gentle bound quiver~$\bar Q$ and its blossoming gentle bound quiver~$\bar Q\blossom$ are represented in \fref{fig:exmBlossomingQuiver}.
\end{example}

The following lemma is immediate and left to the reader.
See \fref{fig:exmBlossomingQuiver}.

@@

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.6]{exmBlossomingQuiver}}
	\caption{A gentle bound quiver~$\bar Q$~(left) and its blossoming gentle bound quiver~$\bar Q\blossom$~(right). Blossom vertices are white and blossom edges are thin.}
	\label{fig:exmBlossomingQuiver}
\end{figure}

@@

\begin{definition}
A \defn{walk} of~$\bar Q$ is a maximal string in~$\bar Q\blossom$ (thus joining two blossom vertices of~$\bar Q\blossom$).
We denote by~$\walks(\bar Q)$ the set of all walks on~$\bar Q$.
Note that~$\walks(\bar Q)$ is finite if and only if~$\bar Q$ has a relation in any (not necessarily oriented) cycle.
As for strings, we often implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and we let~$\walks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \walks(\bar Q)}$ denote the set of undirected~walks.
\end{definition}

\begin{example}
\fref{fig:exmFacet} shows examples of walks on the gentle quiver~$\bar Q$ of \fref{fig:exmBlossomingQuiver}.
\end{example}

@@

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=1.5]{exmBijectionAssociahedron}}
	\caption{An oriented path~$\exmAn$ is simultaneously a triangulation and a grid bound quiver (top). A facet of the reduced non-kissing complex~$\RNKC[\exmAn]$ can be seen as a triangulation or as a collection of non-kissing south-east paths (bottom).}
	\label{fig:exmBijectionAssociahedron}
\end{figure}

@@

\begin{example}
\fref{fig:exmFacet}~(left) gives examples of kissing and non-kissing walks.
%
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.6]{exmFacet}}
	\caption{(Left) Three walks on the quiver~$\bar Q$ of \fref{fig:exmBlossomingQuiver}: the dotted red and orange walks are non-kissing, but both kiss the plain blue walk. (Right) A maximal collection~$F$ of pairwise non-kissing walks on the quiver~$\bar Q$: the thin light blue walks are straight, the others~are~bending.}
	\label{fig:exmFacet}
\end{figure}
\end{example}

@@

\begin{example}
\fref{fig:exmFacet}\,(right) shows a facet~$F$ of the non-kissing complex~$\NKC[\bar Q]$ for the quiver~$\bar Q$ of \fref{fig:exmBlossomingQuiver}.
The reduced non-kissing complexes of all connected gentle bound quivers with~$2$ vertices are illustrated on \fref{fig:all2}.
The reduced non-kissing complexes of two gentle bound quivers with~$3$ vertices are illustrated on \fref{fig:exmNKC}\,(left).
\end{example}

@@

\begin{remark}
Note that the countercurrent order~$\prec_\alpha$
\begin{itemize}
\item is well-defined: if both endpoints of~$\sigma$ are in~$Q_0$, $\mu_\star$ (resp.~$\nu_\star$) should enter and exit~$\sigma$ in the same direction since~$\mu_\star$ and~$\nu_\star$ are non-kissing;
\item is independent of the orientation of~$\mu_\star$ and~$\nu_\star$:~$\mu_\star \prec_\alpha \nu_\star$ iff $(\mu_\star)^{-1} \prec_\alpha \nu_\star$ iff $\mu_\star \prec_\alpha (\nu_\star)^{-1}$; we thus also consider~$\prec_\alpha$ as a relation on undirected marked walks;
\item depends on which occurrence of~$\alpha$ is marked on~$\mu$ and~$\nu$.
\end{itemize}
\end{remark}

@@

\begin{proof}
We prove that~$\prec_\alpha$ is transitive.
Let~$\lambda_\star$, $\mu_\star$, $\nu_\star$ be three pairwise non-kissing walks marked at an occurrence of~$\alpha$ such that~${\lambda_\star \prec_\alpha \mu_\star \prec_\alpha \nu_\star}$. Let~$v$ be a vertex where~$\lambda_\star$ and~$\mu_\star$ split. Then
%Let~$\sigma$ (resp.~$\tau$, resp.~$\rho$) denote the common substring of~$\lambda_\star$ and~$\mu_\star$ (resp.~of~$\mu_\star$ and~$\nu_\star$, resp.~of~$\lambda_\star$ and~$\nu_\star$) containing that occurrence of~$\alpha$. We distinguish two situations:
\begin{itemize}
\item either~$\nu_\star$ contains~$v$, then it must follow~$\mu_\star$ (otherwise~$\nu_\star \prec_\alpha \mu_\star$), so that~$\lambda_\star \prec_\alpha \nu_\star$.
\item or~$\nu_\star$ does not contain~$v$, then~$\nu_\star$ and~$\mu_\star$ split at a vertex~$w$ between~$\alpha$ and~$v$. Since~${\mu_\star \prec_\alpha \nu_\star}$, $\mu$ (and thus~$\lambda$) leaves~$w$ with an arrow in the same direction as~$\alpha$, while~$\nu$ leaves~$w$ with an arrow opposite to the direction of~$\alpha$, so that~$\lambda_\star \prec_\alpha \nu_\star$.
\end{itemize}
Moreover, $\prec_\alpha$ is antisymmetric by definition.
Finally, any two distinct walks of~$F$ marked at an occurrence of~$\alpha$ are comparable in~$\prec_\alpha$.
Therefore, the reflexive closure of~$\prec_\alpha$ defines a total order on the walks of~$F$ marked at an occurrence of~$\alpha$.
\end{proof}

@@

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.6]{exmFlip}}
	\caption{The flip of the orange walk~$\omega$ in the facet~$F$ of \fref{fig:exmFacet}. The other two walks~$\mu, \nu$ of~$F$ involved in the flip are the yellow and green walks. The distinguished arrows on each walk of~$F$ are marked with triple arrows.}
	\label{fig:exmFlip}
\end{figure}
\end{example}

@@

\begin{definition}
\label{def:increasingFlip}
If the common substring~$\sigma$ of~$\omega$ and~$\omega'$ is on top of~$\omega$ and at the bottom of~$\omega'$, then we say that the flip~$F \to F'$ is \defn{increasing} and that the common substring~$\sigma$ is an \defn{ascent} of~$F$ and a \defn{descent} of~$F'$.
We denote by ${\ascents(F) \subseteq \strings^\pm(\bar Q)}$ and $\descents(F) \subseteq \strings^\pm(\bar Q)$ the sets of ascents and descents of~$F$ respectively.
Otherwise,~$\sigma$ is a descent of~$F$ and an ascent of~$F'$ and the flip is called \defn{decreasing}.
\end{definition}

@@

\begin{example}
Oriented flip graphs were studied carefully in~\cite{GarverMcConville, MannevillePilaud-accordion, McConville} for the dissection and grid bound quivers introduced in Section~\ref{subsec:dissectionGridQuivers}.
Note that when the quiver is an oriented path~$\exmAn$, a flip in a facet of the non-kissing complex~$\NKC[\exmAn]$ corresponds to the classical flip of a diagonal in the corresponding triangulation (see \fref{fig:exmBijectionAssociahedron}).
Moreover, the flip is increasing if and only if the slope of the diagonal increases along the flip.
\end{example}

@@

In fact, our proof of Theorem~\ref{thm:lattice} is an adaptation of the proof  developed by T.~McConville in~\cite{McConville}.
Namely, we define a closure operator on subsets of strings whose biclosed sets have a lattice structure~(\ref{sec:biclosedStrings}), define a natural lattice congruence on biclosed sets~(\ref{sec:latticeCongruence}), and show that the Hasse diagram of the lattice quotient is isomorphic to the non-kissing oriented flip graph~(\ref{sec:biclosedSetsToNKF}).
Finally (\ref{sec:nonFriendlyComplex}), we study the join-irreducible elements of the non-kissing lattice~$\NKL$ (Definition~\ref{def:NKL}) and the canonical join complex of~$\NKL$ which we call the non-friendly complex as in~\cite{GarverMcConville-grid}.

@@

\begin{definition}
A \defn{join-representation} of~$x \in L$ is a subset~$J \subseteq L$ such that~${x = \bigJoin J}$.
Such a representation is \defn{irredundant} if~$x \ne \bigJoin J'$ for a strict subset~$J' \subsetneq J$.
The irredundant join-representations of an element~$x \in L$ are ordered by containement of the lower ideals of their elements, \ie~$J \le J'$ if and only if for any~$y \in J$ there exists~$y' \in J'$ such that~$y \le y'$ in~$L$.
The \defn{canonical join-representation} of~$x$ is the minimal irredundant join-representation of~$x$ for this order when it exists.
The \defn{canonical meet-representation} is defined dually.
\end{definition}

@@

\begin{enumerate}[(i)]
\item We have $R \cup \closure{(\closure{\{\sigma\}} \cup \closure{\{\tau\}} )} =   R \cup \closure{\{\sigma,\tau\}}$.
Condition (ii) thus shows that $R \cup \closure{\{\sigma,\tau\}}$ is biclosed.
It follows that $S\vee T = R \cup \closure{\{\sigma,\tau\}}$.

@@

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.45]{exmBiclosed}}
	\caption{Four sets of strings on the gentle bound quiver of \fref{fig:exmBlossomingQuiver}\,(left). The first is neither closed not coclosed, the second is closed but not coclosed, the third is coclosed but not closed, and the fourth is biclosed.}
	\label{fig:exmBiclosed}
\end{figure}
\end{example}

@@

\begin{proof}
The proof is inspired from that of~\cite[Thm.~6.5]{McConville}.
The main difficulty is that~$\Bicl{\bar Q}$ does not satisfies Condition~(i) of Theorem~\ref{thm:characterizationCongruenceUniform} when~$\bar Q$ has a loop.
For example, for the quiver~$\bar Q$ with a single vertex~$v$, a loop~$\alpha$, and the relation~$\alpha^2 = 0$, the biclosed sets of strings are precisely~$\varnothing$ and~$\{\varepsilon_v, \alpha\}$.
We therefore need the adapted criterion of Theorem~\ref{thm:characterizationCongruenceUniform2}.
For a string~$\sigma \in \strings^\pm(\bar Q)$, the closure~$\closure{\{\sigma\}}$ can be of two types:
\begin{itemize}
\item if there is a loop~$\alpha \in Q_1$ such that~$\sigma \alpha \in \strings^\pm(\bar Q)$, then~$\closure{\{\sigma\}} = \{\sigma, \sigma \alpha \sigma^{-1}\}$,
\item otherwise, $\closure{\{\sigma\}} = \{\sigma\}$.
\end{itemize}
In particular, for any two strings~$\sigma, \tau$, the equality~$\closure{\{\sigma\}}=\closure{\{\tau\}}$ implies $\sigma=\tau$.
We note that $\strings^\pm(\bar Q)$ is partially ordered by~$\sigma \vartriangleleft \tau$ if and only if~$\sigma$ is a substring of~$\tau$.

@@

\begin{figure}[h]
	\capstart
	\centerline{
	\begin{overpic}[scale=.45]{exmProjections}
			\put(30,6){$\longleftarrow$}
			\put(31,8){$\projDown$}
			\put(68,6){$\longrightarrow$}
			\put(69,8){$\projUp$}
			\put(12,-3){$\projDown(S)$}
			\put(50,-3){$S$}
			\put(85,-3){$\projUp(S)$}
	\end{overpic}
	}
	\vspace{.3cm}
	\caption{A biclosed set of strings~$S \in \Bicl{\bar Q}$ (middle), where~$\bar Q$ is the bound quiver of \fref{fig:exmBlossomingQuiver}, and its images~$\projDown(S)$ (left) and~$\projUp(S)$ (right) by the down and up projections of Definition~\ref{def:downUpProjections}. For space reasons, $\projUp(S)$ is only represented partially: the remaining strings are obtained by adding independently the two dotted arrows to all strings containing their left endpoint.}
	\label{fig:exmProjections}
\end{figure}
\end{example}

@@

\begin{example}
The map~$\eta$ is illustrated on \fref{fig:exmSurjection}\,(left) for the gentle bound quiver of \fref{fig:exmBlossomingQuiver}\,(left).

\begin{figure}[h]
	\capstart
	\centerline{
	\begin{overpic}[scale=.45]{exmSurjection}
			\put(28,8){$\longrightarrow$}
			\put(29,10){$\eta$}
			\put(69,8){$\longrightarrow$}
			\put(70,10){$\zeta$}
			\put(13,-3){$S$}
			\put(46,-3){$\eta(S)$}
			\put(77,-3){$\zeta(\eta(S)) = \projDown(S)$}
	\end{overpic}
	}
	\vspace{.3cm}
	\caption{The maps~$\eta$ of Definition~\ref{def:eta} from biclosed sets to non-kissing facets (left) and $\zeta$ of Definition~\ref{def:zeta} from non-kissing facets to biclosed sets (right).}
	\label{fig:exmSurjection}
\end{figure}
\end{example}

@@

\begin{example}
The map~$\zeta$ is illustrated on \fref{fig:exmSurjection}\,(right)  for the gentle bound quiver of \fref{fig:exmBlossomingQuiver}\,(left).
\end{example}

@@

\begin{example}
The maps~$\eta$ and~$\zeta$ are illustrated on \fref{fig:exmSurjection}\,(right).
Compare~$\zeta(\eta(S))$ on \fref{fig:exmSurjection}\,(right) with the down projection~$\projDown(S)$ on \fref{fig:exmProjections}\,(left).
\end{example}

@@

\begin{definition}\label{def:NKL}
We call \defn{non-kissing lattice} and denote by~$\NKL$ the transitive closure of the non-kissing oriented flip graph~$\NKG$.
\end{definition}
